---
# Copyright (c) 2018-2019 Intel Corporation
#
# SPDX-License-Identifier: Apache-2.0
title: "Kata Containers Kubernetes metrics report"
author: "Auto generated"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
urlcolor: blue
---

```{r setup, include=FALSE}
#Set these opts to get pdf images which fit into beamer slides better
opts_chunk$set(dev = 'pdf')
# Pick up any env set by the invoking script, such as the root dir of the
# results data tree
source("/inputdir/Env.R")
```
\pagebreak

# Introduction
This report compares the metrics between multiple sets of data generated from
the [Kata Containers report generation scripts](github.com/kata-containers/tests/metrics/report/README.md).

This report was generated using the data from the **`r resultdirs`** results directories.

\pagebreak

# Runtime scaling
This [test](https://github.com/kata-containers/tests/blob/master/metrics/k8s/scaling/k8s_scale.sh)
measures the system memory 'free' reduction and the CPU idle % as it launches more and more
idle `busybox` pods on a single node Kubernetes cluster.

> Note: CPU % is measured as a system whole - 100% represents *all* CPUs on the node.

```{r, echo=FALSE, fig.cap="Memory PSS footprint"}
source('scaling.R')
```
